---
title: "R Notebook"
output: html_notebook
---


```{r}
library(jsonlite)
```


```{r}
x <- fromJSON("https://www.smogon.com/stats/2020-01/chaos/gen8ou-0.json", simplifyDataFrame = TRUE)
```

```{r}
x$info
```


https://www.smogon.com/forums/threads/official-smogon-university-usage-statistics-discussion-thread-mk-2.3508502/

Checks & counters - array of 3 numbers for each pokemon. What do they represent?

Number n of times the matchup occurred (don't count U-Turn KOs or force-outs)
The fraction p of times the counter got the KO or caused a switch
Standard deviation for the previous value: sqrt(p*(1.0-p)/n)

```{r}
x$data$Mandibuzz$`Checks and Counters`$Clefable
```

```{r}
x$data$Mandibuzz$`Viability Ceiling`
```

Teammates
the number in the JSON is the number in the TXT times the pokemon's usage (see chunk below)
```{r}
x$data$Mandibuzz$Teammates$Swoobat
```

Pokemon usage is best calculated by summing abilities - do compare this with usage txt
```{r}
x$data$Mandibuzz$Abilities$bigpecks
x$data$Mandibuzz$Abilities$overcoat
x$data$Mandibuzz$Abilities$weakarmor
```

